### 2023-04-02 main.tex
ii

%%%%%  oscillators
\newcommand{\osc}[1]{\mathbf{#1}}
\newcommand{\oscgreek}[1]{\boldsymbol{#1}}
\newcommand{\dagg}[1]{\bar{#1}}
\newcommand{\ep}{\epsilon}
\newcommand{\ob}{\osc{b}}
\newcommand{\oc}{\osc{c}}
\newcommand{\od}{\osc{d}}
\newcommand{\oab}{\dagg{\osc{a}}}
\newcommand{\obb}{\dagg{\osc{b}}}
\newcommand{\ocb}{\dagg{\osc{c}}}
\newcommand{\odb}{\dagg{\osc{d}}}
\newcommand{\ox}{\oscgreek{\xi}}
\newcommand{\oxb}{\dagg{\oscgreek{\xi}}}
\newcommand{\och}{\oscgreek{\chi}}
\newcommand{\ochb}{\dagg{\oscgreek{\chi}}}
\newcommand{\NN}{\mathbf{N}}
\newcommand{\ccc}{\mathbf{C}}
\newcommand{\qop}{Q}
\newcommand{\sop}{Y}
\newcommand{\q}{\mathbf{\epsilon}}
\newcommand{\ID}{I}
\newcommand{\per}{P}

@@

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Multispecies stirring process
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassek}
 \par\endgroup
\vspace{2em}

@@

At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$. On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space of the process on the graph $G$ is 

@@

\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}^{x}=\twoj\right\}
We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\

@@

\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,\ell=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{\ell}^{x}+\delta_{k}^{y}-\delta_{\ell}^{y})-f(\bm{n})\right]

@@

    \mathcal{L}_{x}f(\bm{n})=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}n_{\ell}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{\ell}^{x})-f(\bm{n})\right]

@@

(\delta_{k}^{x})^{y}_{\ell}=\begin{cases}
1\qquad &\text{if}\quad y=x,\;\ell=k\\

@@

This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{k}^{x}n_{\ell}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{\ell}^{x}$ a particle of type $\ell$ is replaced with a particle of type $k$. 

@@

\alpha_{k}^{x}=\alpha_{k}\qquad \forall x\in V

@@

 \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}

@@

\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}\rho_{k}^{n_{k}^{x}}

@@

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
\end{equation}
%where $\sum_{k=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.

\noindent
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,l=1}^{N}E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$.

@@

\textbf{Remark}:

@@

where the component $r_{k}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
and the component $m_{k}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 

@@

    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}r_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widehat{x}})-f(\bm{\xi})\right)

@@

	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\,\right)

@@

\rho_{k}^{x}:=\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}

@@

On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph. On the other hand, the dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$. This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{k}^{x}$. This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites. In other words the extra-sites play the role of absorbing boundaries. 

@@

\textbf{Remark}: in the reversible situation, i.e. when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}

@@

    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)

@@

$(a^{\dagger})_{k}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\

@@

    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|

@@

\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|

@@

\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}

@@

&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)

@@

\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|

@@

\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}

@@

\frac{(\nu-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}

>>>>

%%%%%  oscillators
\newcommand{\osc}[1]{\mathbf{#1}}
\newcommand{\oscgreea}[1]{\boldsymbol{#1}}
\newcommand{\dagg}[1]{\bar{#1}}
\newcommand{\ep}{\epsilon}
\newcommand{\ob}{\osc{b}}
\newcommand{\oc}{\osc{c}}
\newcommand{\od}{\osc{d}}
\newcommand{\oab}{\dagg{\osc{a}}}
\newcommand{\obb}{\dagg{\osc{b}}}
\newcommand{\ocb}{\dagg{\osc{c}}}
\newcommand{\odb}{\dagg{\osc{d}}}
\newcommand{\ox}{\oscgreek{\xi}}
\newcommand{\oxb}{\dagg{\oscgreek{\xi}}}
\newcommand{\och}{\oscgreek{\chi}}
\newcommand{\ochb}{\dagg{\oscgreek{\chi}}}
\newcommand{\NN}{\mathbf{N}}
\newcommand{\ccc}{\mathbf{C}}
\newcommand{\qop}{Q}
\newcommand{\sop}{Y}
\newcommand{\q}{\mathbf{\epsilon}}
\newcommand{\ID}{I}
\newcommand{\per}{P}

@@

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Multispecies stirring process
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassea}
 \par\endgroup
\vspace{2em}

@@

At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{a}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$. On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space of the process on the graph $G$ is 

@@

\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}
We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$ .\\

@@

\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{a}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-f(\bm{n})\right]

@@

    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\delta_{a}^{x}-\delta_{b}^{x})-f(\bm{n})\right]

@@

(\delta_{a}^{x})^{y}_{b}=\begin{cases}
1\qquad &\text{if}\quad y=x,\;b=k\\

@@

This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $k$. 

@@

\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V

@@

 \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}

@@

\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}

@@

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
\end{equation}
%where $\sum_{a=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{m_{a},n_{a}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.

\noindent
\textbf{Remara}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(E_{al}^{x}-E_{ll}^{x}\right)
\end{equation}
Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$.

@@

\textbf{Remara}:

@@

where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 

@@

    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}r_{a}^{x}\left(f(\bm{\xi}-\delta_{a}^{x}+\delta_{1}^{x}+\delta_{a}^{\widehat{x}})-f(\bm{\xi})\right)

@@

	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)

@@

\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}

@@

On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph. On the other hand, the dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$. This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{a}^{x}$. This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites. In other words the extra-sites play the role of absorbing boundaries. 

@@

\textbf{Remara}: in the reversible situation, i.e. when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\sum_{x\in V}r_{a}^{x}+\sum_{x\in V}m_{a}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}

@@

    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{\widehat{x}}\,E_{1a}^{x}-E_{aa}^{x}\right)

@@

$(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\

@@

    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|

@@

\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|

@@

\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}

@@

&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{a_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{a_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)

@@

\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|

@@

\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}

@@

\frac{(\nu-\sum_{a=2}^{N}r_{a}^{x})}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}
where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{a=2}^{N}r_{a}^{x}$. Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
